Flowchart of Current Algorithm

### 2008-10-12 docs/flowchart/paper.tex
add MarginPar to note that we split scalar_advance
remove the random equations section.  Now instead inline them in the text and cite the equation number from paper III

\section{Equations}

\subsection{Reaction Network}
\begin{eqnarray}
\frac{dX_k}{dt} &=& \omegadot_k(\rho,X_k,T)\enskip, \label{eq:VODE1C} \\
\frac{dT}{dt} &=&\frac{1}{c_p} \left ( -\sum_k \xi_k  \omegadot_k  + \Hnuc \right )\enskip. \label{eq:tempreactC}
\end{eqnarray}

\subsection{Energy}

\begin{equation}
\label{eq:tempenthalpy}
\frac{DT}{Dt} = \frac{1}{\rho c_p} \left[ \left(1 - \rho h_p\right) \frac{D p}{D t}
 - \sum_k \rho \xi_k {\omegadot}_k 
 + \rho \Hnuc + \rho \Hext \right] \enskip , 
\end{equation}

\subsection{Velocity}

\begin{equation}
U = \ut + w_0 \er
\end{equation}

\begin{equation}
\int_{\Omega_H} \ut \cdotb \er \; dA = 0 \label{eq:udoterzero} \enskip ,
\end{equation}

\begin{eqnarray}
\frac{\partial w_0}{\partial t} &=& - w_0 \frac{\partial w_0}{\partial r} - 
\frac{1}{\rho_0} \frac{\partial \pizero}{\partial r} \label{eq:w0upd} \enskip , \\
\frac{\partial\ut}{\partial t} &=& - \ut \cdotb \nablab \ut - w_0 \frac{\partial \ut}{\partial r}
                                 - \left(\ut \cdotb \er\right) \frac{\partial w_0}{\partial r} \er
                                 - \frac{1}{\rho} \nablab\pi
                                 + \frac{1}{\rho_0} \frac{\partial \pizero}{\partial r} \er
                                 - \frac{(\rho-\rhozero)}{\rho} \; g \; \er  \label{eq:utildeupd}  \enskip ,
\end{eqnarray}

\begin{equation}
\label{eq:constraint}
\nablab \cdotb \ubold + \alpha \left( \frac{\partial p_0}{\partial t} + \ubold \cdotb \nablab p_0 \right) =
 -\sigma  \sum_k \xi_k \omegadot_k  + 
  \frac{1}{\rho p_\rho} \sum_k p_{X_k}  {\omegadot}_k + \sigma \Hnuc + \sigma \Hext \equiv S \enskip ,
\end{equation}

\begin{equation}
  S =  -\sigma  \sum_k  \xi_k \omegadot_k  + 
  \frac{1}{\rho p_\rho} \sum_k p_{X_k}  {\omegadot}_k  + \sigma \Hnuc + \sigma \Hext \enskip .
\label{eq:defineS} 
\end{equation}

\begin{equation}
\nablab \cdotb (\beta_0 \ut )  = \beta_0 \left(S - \Sbar \right )
 \enskip .  \label{eq:tildeconstraint}
\end{equation}

\begin{equation}
- \frac{1}{\rho_0} \frac{\partial \pizero}{\partial r} = \frac{\partial w_0}{\partial t} + w_0 \frac{\partial w_0}{\partial r} \enskip, \label{eq:pizero}
\end{equation}

\subsection{Base State}

\begin{eqnarray}
\frac{\partial \rhozero}{\partial t} &=& - \nablab \cdotb \left( \rhozero w_0 \er \right)
- \nablab \cdotb \left( \etarho \er \right) \enskip ,
\label{eq:rho0upd_new}
\end{eqnarray}

\subsubsection{Plane-Parallel}
\begin{equation}
\frac{\partial p_0}{\partial t} = w_0 \rho_0 g  + \etarho g
                                 = - w_0 \frac{\partial p_0}{\partial r} + \etarho g \enskip .
\label{eq:p0upd_new} 
\end{equation}

\begin{equation}
\frac{\partial w_0}{\partial r} =  \Sbar - \frac{1}{\gammabar p_0} \etarho g \enskip \label{eq:divw0} ,
\end{equation}

\subsection{Misc.}

\begin{equation}
w_0^{n,\star} = \frac{\dt^{n} w_0^{\nmh} + \dt^{n-1} w_0^{\nph,\star}}{\dt^n+\dt^{n-1}}\enskip,\label{eq:w0nstar}
\end{equation}
\begin{equation}
\left(\frac{\partial w_0}{\partial r}\right)^{n,\star} = \frac{1}{\dt^n+\dt^{n-1} } \left [ \dt^{n} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nmh}
+ \dt^{n-1} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nph,\star} \right ] \enskip.\label{eq:dw0drnstar}
\end{equation}

\begin{equation}
 L_\beta^\rho \phi =
   D \left ( \beta_0^{\nph} {\bf V} \right) - \beta_0^{\nph} \left(S^{n+1}-\overline{S}^{n+1} \right)\enskip,
\label{eq:nodal_solve}
\end{equation}

@@

\item {\bf React State}$[\rho^{\inp},(\rho h)^{\inp},X_k^{\inp},T^{\inp}, (\rho\Hext)^{\inp}]\rightarrow$
$[\rho^{\outp}, (\rho h)^{\outp}, X_k^{\outp}, T^{\outp}, (\rho \omegadot_k)^{\outp}]$ \newline
is the process by which we evolve the species and enthalpy from $X_k^{\inp} \rightarrow X_k^{\outp}$ 
and $(\rho h)^{\inp} \rightarrow (\rho h)^{\outp}$ by solving the following system of equations 
over a time interval of  $\Delta t/2$,
\begin{eqnarray}
\frac{\partial X_k}{\partial t} &=& \omegadot_k\enskip,\\
\frac{\partial (\rho h)}{\partial t} &=& \rho \Hnuc + \rho \Hext\enskip .
\end{eqnarray}
  In particular, to evolve the species, we solve the system:
\begin{eqnarray}
\frac{dX_k}{dt} &=& \omegadot_k(\rho,X_k,T)\enskip, \\
\frac{dT}{dt} &=&\frac{1}{c_p} \left ( -\sum_k \xi_k  \omegadot_k  + \Hnuc \right )\enskip.
\end{eqnarray}
using the stiff ordinary differential equation
 integration methods provided by the {\tt VODE} package (cite VODE).
The absolute error tolerances are set to $10^{-12}$ for the species,
 and a relative tolerance of $10^{-5}$ is used for the temperature.  
The integration yields the new values of the mass fractions, $X_k^{\outp}$.  
Equation (\ref{eq:tempreactC}) is derived from equation (\ref{eq:tempenthalpy}) by assuming that the pressure is constant during the burn state.  
In evolving these equations, we need to evaluate $c_p$ and $\xi_k$.  
In theory, this means evaluating the equation of state for each right-hand side evaluation that {\tt VODE} requires.  
In practice, we freeze $c_p$ and $\xi_k$ at the start of the integration time step and compute them using 
$\rho^{\inp}, X_k^{\inp},$ and $T^{\inp}$ as inputs to the equation of state.  
We note that while temperature is evolved when solving these equations, we do not keep the final temperature, 
nor do we use it to compute the final change in enthalpy.  
Therefore, $T^{\outp} = T^{\inp}$.  Also, note that the density remains unchanged during 
the {\bf React State} step, i.e., $\rho^{\outp} = \rho^{\inp}$.

@@

\item {\bf Advect Base}$(\rho_0^{\inp}, p_0^{\inp}, \beta_0^{\inp}, w_0^{\inp}, \psi^{\inp} ) \rightarrow 
(\rho_0^{\outp}, \rho_0^{\outp,n+\myhalf}, p_0^{\outp})$ 
\newline
is the process by which we update the base state through $\dt$ in time given the
radial velocity $w_0^{\inp}.$ Here we discuss
the algorithm for plane-parallel geometries.  
The base state arrays are all one-dimensional 
in the radial coordinate; we think of the base state quantities as defined
at cell centers, with $w_0$ and $\beta_0$ defined halfway in-between.\\ \\
a)  For the density update, we discretize equation (\ref{eq:rho0upd_new}), neglecting the $\etarho$ term,
to compute the new base state density,
\begin{eqnarray}
\rho_{0,j}^{\outp} &=& \rho_{0,j}^{\inp} - \frac{\dt}{\dr} 
\left [ \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j+\myhalf} -  
         \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j-\myhalf} \right ] \nonumber  \enskip,
\end{eqnarray}
where $j$ refers to the one-dimensional index in the radial direction.
The interface states, ${{\rho}_0}^{\outp,\nph}$, are found via the procedure described in
paper II, Appendix A, and are saved for use later in the overall algorithm.\\ \\
b)  For the pressure update, We discretize equation (\ref{eq:p0upd_new}), 
to compute the new base state pressure,
\begin{eqnarray}
p_{0,j}^\outp &=& p_{0,j}^\inp - \frac{\dt}{2\dr} \left (w_{0,j+\myhalf}^\inp
+ w_{0,j-\myhalf}^\inp \right)
\left (p_{0,j+\myhalf}^{n+\myhalf} -p_{0,j-\myhalf}^{n+\myhalf} \right ) + \dt \; \psi_j^\inp \enskip,
\end{eqnarray}
where the interface states are again found via the procedure described in
paper II, Appendix A.\\ \\
c)  For the enthalpy update, \MarginPar{We need enthalpy equations now that we are predicting $(\rho h)'$.}
\\

@@

\item At the beginning of each time step, we need an estimate for the time-centered
source term in the velocity divergence constraint (see eq. [\ref{eq:constraint}]).
If this is the first step of the calculation ($n=0$), we set
\[
S^{\half,\star} = \frac{S^0 + S^1}{2} \enskip ,
\]
where $S^1$ is found through the iterative process that initializes the calculation.
Otherwise, following the method used in our small-scale low Mach number algorithm
(Cite Bell04), we extrapolate to the half-time using the source
terms at the previous and current time levels
\begin{equation}
S^{\nph,\star} = S^n + \frac{\Delta t^n}{2} \frac{S^n - S^{n-1}}{\Delta t^{n-1}} \enskip .
\end{equation}

@@

\item Construct $w_0^{\nph,\star}$ by integrating equation (\ref{eq:divw0}) using 
the lagged $\psi^{\nmh},$
\MarginPar{Need dpdt\_factor stuff.}
\begin{equation}
\frac{\partial w_0^{\nph,\star}}{\partial r} =  \overline{S}^{\nph,\star} 
- \frac{1}{\gammabar^{n} p_0^{n}} \psi^{\nmh} \enskip . \nonumber
\end{equation}
For spherical geometries, this equation would be modified.

\item Using equation (\ref{eq:pizero}), define the scaled pressure gradient
\begin{equation}
-\left ( \frac{1}{\rho_0^n} \frac{\partial \pizeroone}{\partial r} \right ) = 
\frac{w_0^{\nph,\star} - w_0^\nmh}{(\dt^n+\dt^{n-1})/2} 
+  w_0^{n,\star} \left(\frac{\partial w_0}{\partial r}\right)^{n,\star} \enskip ,
\end{equation} 
where $w_0^{n,\star}$ and $(\partial w_0 / \partial r)^{n,\star}$ are
\begin{equation}
w_0^{n,\star} = \frac{\dt^{n} w_0^{\nmh} + \dt^{n-1} w_0^{\nph,\star}}{\dt^n+\dt^{n-1}}\enskip,\end{equation}
\begin{equation}
\left(\frac{\partial w_0}{\partial r}\right)^{n,\star} = \frac{1}{\dt^n+\dt^{n-1} } \left [ \dt^{n} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nmh}
+ \dt^{n-1} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nph,\star} \right ] \enskip.\end{equation}
If $n=0$, we use $\dt^{-1} = \dt^0$.

@@

The procedure to construct $\uadvone$ is described in detail in Appendix B of paper III.
We note that  $\uadvone$ satisfies the discrete versions of equations
(\ref{eq:udoterzero}) and (\ref{eq:tildeconstraint}), in particular,
\MarginPar{Need dpdt\_factor stuff.}
\begin{equation}
\nablab \cdotb \left(\beta_0^n \uadvone\right) = \beta_0^n \left(S^{\nph,\star} - \overline{S}^{\nph,\star}\right)
\enskip ,
\end{equation}

@@

\item Compute the edge states, $(\rho X_k)^{(1),\nph,\star}$ and $(\rho h)^{(1),\nph,\star},$
      for the conservative update of $(\rho X_k)$ and $(\rho h).$  Here we
      predict $\rho'$, $(\rho h)'$, and $X_k$ to the edges, using
      a second-order Taylor expansion in space and time, as described in
      paper II, Appendix A, using $\V = \uadvone+w_0^{\nph,\star} \er$.  
      We do not include the reaction terms in the enthalpy prediction, 
      since we accounted for them already in {\bf React State}. 
      We use the base state density, $\rho_0$, and base state enthalpy, $(\rho h)_0$,
      to convert these to edge states for $(\rho X_k)$ and $(\rho h)$. 
      We define $\rho^{(1),\nph,\star} = \sum_k (\rho X_k)^{(1),\nph,\star}.$

@@

\item Construct $w_0^{\nph}$ by integrating equation (\ref{eq:divw0}),
\MarginPar{Need dpdt\_factor stuff.}
\begin{equation}
\frac{\partial w_0^{\nph}}{\partial r} =  \overline{S}^{\nph,\star} - \frac{1}{\gammabar^{\nph,\star} p_0^{\nph,\star}} \psi^{\nph,\star} \enskip , \nonumber
\end{equation}
for plane-parallel geometries, where 
$\gammabar^{\nph,\star} = (\gammabar^{n} + \gammabar^{n+1,\star} ) / 2 $ and
$ p_0^{\nph,\star} = (p_0^{n} + p_0^{n+1,\star} ) / 2.$

\item Using equation (\ref{eq:pizero}), define
\begin{equation}
-\left ( \frac{1}{\rho_0^n} \frac{\partial \pizerotwo}{\partial r} \right ) = 
\frac{w_0^{\nph} - w_0^\nmh}{\myhalf(\dt^n+\dt^{n-1})} 
+ w_0^n \left(\frac{\partial w_0}{\partial r}\right)^n.
\end{equation}
where $w_0^n$ and $(\partial w_0 / \partial r)^{n}$ are defined analogously to 
equations (\ref{eq:w0nstar}) and (\ref{eq:dw0drnstar}).

@@

The velocity update happens analogously to paper II, using $S^{n+1}$ from step 10.
We update the velocity field $\ut^n$ to $\ut^{n+1,\star}$ by discretizing
equation (\ref{eq:utildeupd}), 
\begin{eqnarray}
\ut^{n+1,\star} &=& \ut^n - \dt \;
 \left[\left((\uadvtwo+ w_0^{\nph} \er) \cdotb \nablab\right) \ut \right]^\nph
      - \dt \; \left(\uadvtwo \cdotb \er\right)  \left(\frac{\partial w_0^{\nph}}{\partial r} \right) \er \nonumber \\
   &&   + \dt \left[ - \frac{1}{\rho^\nph} {\mathbf{G}} \pi^\nmh
        + \frac{1}{\rho_0} {\mathbf{G}} \pizerotwo
        - \frac{(\rho^\nph-\rhozero^\nph)}{\rho^\nph} g \er \right] \enskip ,
\end{eqnarray}
where $\rho^\nph = ( \rho^n + \rho^{n+1} )/2$
and $\mathbf{G}$ approximates a cell-centered gradient from nodal data. 
The construction of $\left[((\uadvtwo+ w_0^{\nph} \er) \cdotb \nablab) \ut \right]^\nph$
is described in paper II, Appendix A, with $\V = \uadvtwo+w_0^{\nph} \er$ and~$s$ set to each
component of $\ut^n$ individually.

Finally, we impose the divergence constraint from equation (\ref{eq:tildeconstraint}),
\MarginPar{Need dpdt\_factor stuff.}
\[
\nablab \cdotb \left(\beta_0^{\nph} \ut^{n+1} \right)  = \beta_0^{\nph} \left(S^{n+1} - \overline{S}^{n+1} \right)\enskip,
\]
by defining ${\bf V} = \ut^{n+1,\star} + ( \dt / \rho^\nph ) \; \mathbf{G} \pi^\nmh$ and solving
\begin{equation}
 L_\beta^\rho \phi =
   D \left ( \beta_0^{\nph} {\bf V} \right) - \beta_0^{\nph} \left(S^{n+1}-\overline{S}^{n+1} \right)\enskip,
\end{equation}
for nodal values of $\phi$, where
$\beta_0^\nph = ( \beta_0^n + \beta_0^{n+1} )/2$ and
$L_\beta^\rho$ is the standard bilinear
finite element approximation to $\nablab \cdotb ({\beta_0^\nph}/{\rho^\nph}) \nablab.$
In this step, $D$ is a discrete second-order operator that approximates the 
divergence at nodes from cell-centered data and satisfies
$\mathbf{G} = -D^T.$ 
(See (cite almgrenBellSzymczak:1996) for a detailed discussion of this
approximate projection; see (cite almgren:bell:crutchfield) for a discussion
of this particular form of the projection operand.)  
We solve the linear system of equation (\ref{eq:nodal_solve}) using multigrid V-cycles with Gauss-Seidel relaxation.

>>>>

@@

\item {\bf React State}$[\rho^{\inp},(\rho h)^{\inp},X_k^{\inp},T^{\inp}, (\rho\Hext)^{\inp}]\rightarrow$
$[\rho^{\outp}, (\rho h)^{\outp}, X_k^{\outp}, T^{\outp}, (\rho \omegadot_k)^{\outp}]$ \newline
is the process by which we evolve the species and enthalpy from $X_k^{\inp} \rightarrow X_k^{\outp}$ 
and $(\rho h)^{\inp} \rightarrow (\rho h)^{\outp}$ by solving the following system of equations 
over a time interval of  $\Delta t/2$,
\begin{eqnarray}
\frac{\partial X_k}{\partial t} &=& \omegadot_k\enskip,\\
\frac{\partial (\rho h)}{\partial t} &=& \rho \Hnuc + \rho \Hext\enskip .
\end{eqnarray}
  In particular, to evolve the species, we solve the system:
\begin{eqnarray}
\frac{dX_k}{dt} &=& \omegadot_k(\rho,X_k,T)\enskip, \\
\frac{dT}{dt} &=&\frac{1}{c_p} \left ( -\sum_k \xi_k  \omegadot_k  + \Hnuc \right )\enskip. \label{eq:reacttemp}
\end{eqnarray}
using the stiff ordinary differential equation integration methods
provided by the {\tt VODE} package (cite VODE).  The absolute error
tolerances are set to $10^{-12}$ for the species, and a relative
tolerance of $10^{-5}$ is used for the temperature.  The integration
yields the new values of the mass fractions, $X_k^{\outp}$.  Equation
(\ref{eq:reacttemp}) is derived from the full temperature evolution equation
\begin{equation}
\label{eq:tempenthalpy}
\frac{DT}{Dt} = \frac{1}{\rho c_p} \left[ \left(1 - \rho h_p\right) \frac{D p}{D t}
 - \sum_k \rho \xi_k {\omegadot}_k 
 + \rho \Hnuc + \rho \Hext \right] \enskip , 
\end{equation}
(paper III; eq.~[8])
by assuming that the pressure is constant during the burn state.  In
evolving these equations, we need to evaluate $c_p$ and $\xi_k$.  In
theory, this means evaluating the equation of state for each
right-hand side evaluation that {\tt VODE} requires.  In practice, we
freeze $c_p$ and $\xi_k$ at the start of the integration time step and
compute them using $\rho^{\inp}, X_k^{\inp},$ and $T^{\inp}$ as inputs
to the equation of state.  We note that while temperature is evolved
when solving these equations, we do not keep the final temperature,
nor do we use it to compute the final change in enthalpy.  Therefore,
$T^{\outp} = T^{\inp}$.  Also, note that the density remains unchanged
during the {\bf React State} step, i.e., $\rho^{\outp} = \rho^{\inp}$.

@@

\item {\bf Advect Base}$(\rho_0^{\inp}, p_0^{\inp}, \beta_0^{\inp}, w_0^{\inp}, \psi^{\inp} ) \rightarrow 
(\rho_0^{\outp}, \rho_0^{\outp,n+\myhalf}, p_0^{\outp})$ 
\newline
is the process by which we update the base state through $\dt$ in time \MarginPar{we need a separate section for spherical}
given the radial velocity $w_0^{\inp}.$ Here we discuss the algorithm
for plane-parallel geometries.  The base state arrays are all
one-dimensional in the radial coordinate; we think of the base state
quantities as defined at cell centers, with $w_0$ and $\beta_0$
defined halfway in-between.\\ \\ a) For the density update, we
discretize equation the base state density evolution equation
\begin{eqnarray}
\frac{\partial \rhozero}{\partial t} &=& - \nablab \cdotb \left( \rhozero w_0 \er \right)
- \nablab \cdotb \left( \etarho \er \right) \enskip ,
\label{eq:rho0upd_new}
\end{eqnarray}
(paper III; eq.~[29]), neglecting the $\etarho$ term, to compute the
new base state density,
\begin{eqnarray}
\rho_{0,j}^{\outp} &=& \rho_{0,j}^{\inp} - \frac{\dt}{\dr} 
\left [ \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j+\myhalf} -  
         \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j-\myhalf} \right ] \nonumber  \enskip,
\end{eqnarray}
where $j$ refers to the one-dimensional index in the radial direction.
The interface states, ${{\rho}_0}^{\outp,\nph}$, are found via the
procedure described in paper II, Appendix A, and are saved for use
later in the overall algorithm.\\ \\ b) For the pressure update, we
discretize the base state pressure evolution equation,
\begin{equation}
\frac{\partial p_0}{\partial t} = w_0 \rho_0 g  + \etarho g
                                 = - w_0 \frac{\partial p_0}{\partial r} + \etarho g \enskip .
\label{eq:p0upd_new}
\end{equation}
(paper III; eq.~[31]) to compute the new base state pressure,
\begin{eqnarray}
p_{0,j}^\outp &=& p_{0,j}^\inp - \frac{\dt}{2\dr} \left (w_{0,j+\myhalf}^\inp
+ w_{0,j-\myhalf}^\inp \right)
\left (p_{0,j+\myhalf}^{n+\myhalf} -p_{0,j-\myhalf}^{n+\myhalf} \right ) + \dt \; \psi_j^\inp \enskip,
\end{eqnarray}
where the interface states are again found via the procedure described in
paper II, Appendix A.\\ \\
c)  For the enthalpy update, \MarginPar{We need enthalpy equations now that we are predicting $(\rho h)'$.}
\\

@@

\item At the beginning of each time step, we need an estimate for the time-centered
source term in the velocity divergence constraint,
\begin{equation}
  S =  -\sigma  \sum_k  \xi_k \omegadot_k  + 
  \frac{1}{\rho p_\rho} \sum_k p_{X_k}  {\omegadot}_k  + \sigma \Hnuc + \sigma \Hext \enskip ,
\label{eq:defineS} 
\end{equation}
(paper III; eq.~[19]).

If this is the first step of the calculation ($n=0$), we set
\[
S^{\half,\star} = \frac{S^0 + S^1}{2} \enskip ,
\]
where $S^1$ is found through the iterative process that initializes the calculation.
Otherwise, following the method used in our small-scale low Mach number algorithm
(Cite Bell04), we extrapolate to the half-time using the source
terms at the previous and current time levels
\begin{equation}
S^{\nph,\star} = S^n + \frac{\Delta t^n}{2} \frac{S^n - S^{n-1}}{\Delta t^{n-1}} \enskip .
\end{equation}

@@

\item Construct $w_0^{\nph,\star}$ by integrating
\begin{equation}
\frac{\partial w_0}{\partial r} =  \Sbar - \frac{1}{\gammabar p_0} \etarho g \enskip \label{eq:divw0} ,
\end{equation}
using the lagged $\psi^{\nmh},$ \MarginPar{note: this is true only for plane-parallel}
\MarginPar{Need dpdt\_factor stuff.}
\begin{equation}
\frac{\partial w_0^{\nph,\star}}{\partial r} =  \overline{S}^{\nph,\star} 
- \frac{1}{\gammabar^{n} p_0^{n}} \psi^{\nmh} \enskip . \nonumber
\end{equation}
For spherical geometries, this equation would be modified.

\item Using 
\begin{equation}
- \frac{1}{\rho_0} \frac{\partial \pizero}{\partial r} = \frac{\partial w_0}{\partial t} + w_0 \frac{\partial w_0}{\partial r} \enskip, \label{eq:pizero}
\end{equation}
define the scaled pressure gradient
\begin{equation}
-\left ( \frac{1}{\rho_0^n} \frac{\partial \pizeroone}{\partial r} \right ) = 
\frac{w_0^{\nph,\star} - w_0^\nmh}{(\dt^n+\dt^{n-1})/2} 
+  w_0^{n,\star} \left(\frac{\partial w_0}{\partial r}\right)^{n,\star} \enskip ,
\end{equation} 
where $w_0^{n,\star}$ and $(\partial w_0 / \partial r)^{n,\star}$ are
\begin{equation}
w_0^{n,\star} = \frac{\dt^{n} w_0^{\nmh} + \dt^{n-1} w_0^{\nph,\star}}{\dt^n+\dt^{n-1}}\enskip,\end{equation}
\begin{equation}
\left(\frac{\partial w_0}{\partial r}\right)^{n,\star} = \frac{1}{\dt^n+\dt^{n-1} } \left [ \dt^{n} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nmh}
+ \dt^{n-1} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nph,\star} \right ] \enskip.\end{equation}
If $n=0$, we use $\dt^{-1} = \dt^0$.

@@

The procedure to construct $\uadvone$ is described in detail in Appendix B of paper III.
We note that  $\uadvone$ satisfies the discrete versions of 
\begin{equation}
\int_{\Omega_H} \ut \cdotb \er \; dA = 0 \label{eq:udoterzero} 
\end{equation}
(paper III; eq.~[21])
and
\begin{equation}
\nablab \cdotb (\beta_0 \ut )  = \beta_0 \left(S - \Sbar \right )
\label{eq:tildeconstraint}
\end{equation}
(paper III; eq.~[39]).
In particular,
\MarginPar{Need dpdt\_factor stuff.}
\begin{equation}
\nablab \cdotb \left(\beta_0^n \uadvone\right) = \beta_0^n \left(S^{\nph,\star} - \overline{S}^{\nph,\star}\right)
\enskip ,
\end{equation}

@@

\item Compute the edge states, $(\rho X_k)^{(1),\nph,\star}$ and $(\rho h)^{(1),\nph,\star},$
      for the conservative update of $(\rho X_k)$ and $(\rho h).$  Here we
      predict $\rho'$, $(\rho h)'$, and $X_k$ to the edges, using
      a second-order Taylor expansion in space and time, as described in
      paper II, Appendix A, using $\V = \uadvone+w_0^{\nph,\star} \er$.  
      We do not include the reaction terms in the enthalpy prediction, 
      since we accounted for them already in {\bf React State}. 
      We use the base state density, $\rho_0$, and base state enthalpy, $(\rho h)_0$,
      to convert these to edge states for $(\rho X_k)$ and $(\rho h)$. 
      We define $\rho^{(1),\nph,\star} = \sum_k (\rho X_k)^{(1),\nph,\star}.$  \MarginPar{we actually split these now, and do $\rho$ first, compute $\psi$, and then do $(\rho h)$}

@@

\item Construct $w_0^{\nph}$ by integrating equation (\ref{eq:divw0}),
\MarginPar{this is plane-parallel only}
\MarginPar{Need dpdt\_factor stuff.}
\begin{equation}
\frac{\partial w_0^{\nph}}{\partial r} =  \overline{S}^{\nph,\star} - \frac{1}{\gammabar^{\nph,\star} p_0^{\nph,\star}} \psi^{\nph,\star} \enskip , \nonumber
\end{equation}
for plane-parallel geometries, where 
$\gammabar^{\nph,\star} = (\gammabar^{n} + \gammabar^{n+1,\star} ) / 2 $ and
$ p_0^{\nph,\star} = (p_0^{n} + p_0^{n+1,\star} ) / 2.$

\item Using equation (\ref{eq:pizero}), define
\begin{equation}
-\left ( \frac{1}{\rho_0^n} \frac{\partial \pizerotwo}{\partial r} \right ) = 
\frac{w_0^{\nph} - w_0^\nmh}{\myhalf(\dt^n+\dt^{n-1})} 
+ w_0^n \left(\frac{\partial w_0}{\partial r}\right)^n.
\end{equation}
where $w_0^n$ and $(\partial w_0 / \partial r)^{n}$ are defined through
\begin{equation}
w_0^{n,\star} = \frac{\dt^{n} w_0^{\nmh} + \dt^{n-1} w_0^{\nph,\star}}{\dt^n+\dt^{n-1}}\enskip,\label{eq:w0nstar}
\end{equation}
(paper III; eq.~[53]) and
\begin{equation}
\left(\frac{\partial w_0}{\partial r}\right)^{n,\star} = \frac{1}{\dt^n+\dt^{n-1} } \left [ \dt^{n} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nmh}
+ \dt^{n-1} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nph,\star} \right ] \enskip.\label{eq:dw0drnstar}
\end{equation}
(paper III; eq.~[54]).

@@

The velocity update happens analogously to paper II, using $S^{n+1}$ from step 10.
We update the velocity field $\ut^n$ to $\ut^{n+1,\star}$ by discretizing
\begin{equation}
\frac{\partial\ut}{\partial t} = - \ut \cdotb \nablab \ut - w_0 \frac{\partial \ut}{\partial r}
                                 - \left(\ut \cdotb \er\right) \frac{\partial w_0}{\partial r} \er
                                 - \frac{1}{\rho} \nablab\pi
                                 + \frac{1}{\rho_0} \frac{\partial \pizero}{\partial r} \er
                                 - \frac{(\rho-\rhozero)}{\rho} \; g \; \er  \label{eq:utildeupd}  \enskip\
 ,
\end{equation}
(paper III; eq.~[37]) as 
\begin{eqnarray}
\ut^{n+1,\star} &=& \ut^n - \dt \;
 \left[\left((\uadvtwo+ w_0^{\nph} \er) \cdotb \nablab\right) \ut \right]^\nph
      - \dt \; \left(\uadvtwo \cdotb \er\right)  \left(\frac{\partial w_0^{\nph}}{\partial r} \right) \er \nonumber \\
   &&   + \dt \left[ - \frac{1}{\rho^\nph} {\mathbf{G}} \pi^\nmh
        + \frac{1}{\rho_0} {\mathbf{G}} \pizerotwo
        - \frac{(\rho^\nph-\rhozero^\nph)}{\rho^\nph} g \er \right] \enskip ,
\end{eqnarray}
where $\rho^\nph = ( \rho^n + \rho^{n+1} )/2$
and $\mathbf{G}$ approximates a cell-centered gradient from nodal data. 
The construction of $\left[((\uadvtwo+ w_0^{\nph} \er) \cdotb \nablab) \ut \right]^\nph$
is described in paper II, Appendix A, with $\V = \uadvtwo+w_0^{\nph} \er$ and~$s$ set to each
component of $\ut^n$ individually.

Finally, we impose the divergence constraint from equation (\ref{eq:tildeconstraint}),
\MarginPar{Need dpdt\_factor stuff.}
\[
\nablab \cdotb \left(\beta_0^{\nph} \ut^{n+1} \right)  = \beta_0^{\nph} \left(S^{n+1} - \overline{S}^{n+1} \right)\enskip,
\]
by defining ${\bf V} = \ut^{n+1,\star} + ( \dt / \rho^\nph ) \; \mathbf{G} \pi^\nmh$ and solving
\begin{equation}
 L_\beta^\rho \phi =
   D \left ( \beta_0^{\nph} {\bf V} \right) - \beta_0^{\nph} \left(S^{n+1}-\overline{S}^{n+1} \right)\enskip,
\end{equation}
for nodal values of $\phi$, where
$\beta_0^\nph = ( \beta_0^n + \beta_0^{n+1} )/2$ and
$L_\beta^\rho$ is the standard bilinear
finite element approximation to $\nablab \cdotb ({\beta_0^\nph}/{\rho^\nph}) \nablab.$
In this step, $D$ is a discrete second-order operator that approximates the 
divergence at nodes from cell-centered data and satisfies
$\mathbf{G} = -D^T.$ 
(See (cite almgrenBellSzymczak:1996) for a detailed discussion of this
approximate projection; see (cite almgren:bell:crutchfield) for a discussion
of this particular form of the projection operand.)  
We solve the linear system of equation
\begin{equation}
 L_\beta^\rho \phi =
   D \left ( \beta_0^{\nph} {\bf V} \right) - \beta_0^{\nph} \left(S^{n+1}-\overline{S}^{n+1} \right)\enskip,
\label{eq:nodal_solve}
\end{equation}
(paper III; eq.~[77]) using multigrid V-cycles with Gauss-Seidel relaxation.
